Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-02-27 2017-inl-ldrd.tex
inl ldrd draft

\paragraph{Our current work} models the transient, three-dimensional, multi-scale physics
of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}, and \gls{FHR} designs.  
This work is well underway with our development of the Moltres application 
\cite{lindsay_moltres_2017}, which relies on the \gls{MOOSE} framework \cite{gaston_moose:_2009}. 
Initial steady state simulations of the \gls{MSRE} have leveraged the Blue Waters 
supercomputer to establish successful coupling between neutronics and thermal 
hydraulics using the \gls{ARFC}-developed Moltres tool. Validation and 
verification efforts are ongoing and upcoming transient simulations seek to explore 
parameters that might increase \gls{LOFC}, \gls{LOHS}, and \gls{RIA} 
survivability in novel reactors.

>>>>

\paragraph{Our current work} models the transient, three-dimensional, multi-scale physics
of promising molten salt reactors such as the \gls{MSRE}, \gls{MSBR}.
This work is well underway with our development of the Moltres application 
\cite{lindsay_moltres_2017}. Moltres relies on the \gls{MOOSE} framework 
\cite{gaston_moose:_2009} as well as its Navier-Stokes capabilities. These 
existing tools are extended with multi-group diffusion neutronics, . 
Initial steady state simulations of the \gls{MSRE} have leveraged the Blue Waters 
supercomputer to establish successful coupling between neutronics and thermal 
hydraulics using the \gls{ARFC}-developed Moltres tool. Validation and 
verification efforts are ongoing and upcoming transient simulations seek to explore 
parameters that might increase \gls{LOFC}, \gls{LOHS}, and \gls{RIA} 
survivability in novel reactors.
